class: center, middle

## Environments

???
Up until now, I've mentioned _environments_ a lot.

They are, put shortly, kinda like lists, but

- have unique names
- have unordered elements
- have parent environments
- are _not_ copied when modified

---

## Lexical scoping

???
Lexical scoping referes to how R looks up values for symbols you use in function calls.

This is another thing R has inherited from Lisp.  
It looks up symbols based on how functions were nested when they were created (not called)

When a function is called

1. R looks up its arguments in the environment where the function is defined
2. If it doesn't find it, it goes to the parent environment
3. If it ends up in the `emptyenv`, the ancestor of all environments, it throws an error

--

.pull-left[
```{r}
f1 <- function() {
  b <- 2
  f2 <- function() {
    c <- 3
    f3 <- function() {
      a + b + c
    }
    f3()
  }
  f2()
}
```
]

???
Here is an example with three nested functions

--

.pull-right[
```{r, error=TRUE}
f1()
a <- 1
f1()
```

]

???
When we call it, R starts looking up symbols from the innermost function environment.

At first, since it doesn't find `a`, it throws an error.  
But if we define `a` in the global environment, it returns a value.
