---
title: "Non-Standard Evaluation"
subtitle: "and Metaprogramming in R"
author: "<a href='https://github.com/janusvm'>Janus Valberg-Madsen</a>"
date: "`r Sys.Date()` @ Aalborg R User Group"
output:
  xaringan::moon_reader:
    css: [default, default-fonts, custom.css]
    lib_dir: libs
    nature:
      highlightStyle: monokai-sublime  # gruvbox-light
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  fig.align = 'center'
)

# Utility functions
script <- function(file) source(file.path("..", "scripts", file))
fig <- function(file) file.path("index_files", "figure-html", file)
fa <- function(icon) paste0('<i class="fa fa-', icon, '"></i>')

# Check dependencies
script("deps.R")
```

```{r pkgs}
library(rlang)
```

--

```{r}
e1 <- expr(y <- 2 * x)
e2 <- expr(`<-`(y, `*`(2, x)))
identical(e1, e2)
```

--

```{r, echo=FALSE, fig.align='center', out.width='50%'}
filename <- fig("simple-ast.svg")
jsvm::expr2tikz(!!e1, filename)
knitr::include_graphics(filename)
```

???
Here is a graphical representation of what's going on, called an _abstract syntax tree (AST)_.  
The orange squares represent calls; first child is the function being called, subsequent children are arguments.

---

# Everything is a function

.pull-left[
```{r}
e1 <- expr(1)
e2 <- expr(({1}))
```
]

---

count: false

# Everything is a function

.pull-left[
```{r}
e1 <- expr(1)
e2 <- expr(({1}))
```

```{r}
identical(eval(e1), eval(e2))
identical(e1, e2)
```
]

--

.pull-right[
```{r, echo=FALSE, out.width='75%'}
filename <- fig("parens-ast.svg")
jsvm::expr2tikz(!!e2, filename)
knitr::include_graphics(filename)
```
]

---

# Links


`r emo::ji("closed_book")` [Advanced R](https://adv-r.hadley.nz) by Hadley Wickham (online book)

`r fa("github")` [repository](https://github.com/AalborgRUG/talk-nse) for this presentation with source code and extra notes

`r emo::ji("package")` [xaringan](https://github.com/yihui/xaringan), used to make these slides (`remark.js` wrapper for R)

`r emo::ji("package")` [jsvm](https://github.com/janusvm/jsvm), used for producing the AST figures (developed by yours truly `r {emo::ji("smirk")}`)

---

class: inverse, middle, center

# `r {emo::ji("sparkles")}` Thank you for your time `r {emo::ji("sparkles")}`
